Algorithms for Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2014-09-29 paper/paper.tex
Update text for corrected SPSS example

The deadline of a task $t$ is then:
%
$$
DL(t) = LST(t) + RT(t) + ST(Level(t))
$$
%
where $Level(t)$ is the level of $t$, $RT(t)$ is the runtime of $t$, and 
$LST(t)$ is the latest start time of $t$ determined by:
%
$$
LST(t) = \begin{cases}
0,&$if~$Pred(t) = \emptyset\cr
\max_{p \in Pred(t)} DL(p),&$otherwise.$
\end{cases}
$$

@@

To illustrate how the algorithms perform, we parepared an artificial ensemble 
of three workflows, as seen in Fig.~\ref{fig:example-ensemble}. 
The deadline is set to 6 hours and the budget to \$18. In this example we assume
that there are no VM provisioning delays, the runtime estimates are accurate, 
there are no failures and the cost of 1 VM-hour is \$1.
For dynamic algorithms we assume that the low utilization threshold ($u_l$) for deprovisioning is 50\%
and that the autoscaling parameter $v_{max} = 1$.

@@

The resulting schedule produced by SPSS algorithm is shown in
Fig.~\ref{fig:algorithms-example-spss}. SPSS generates the schedule by
considering workflows in priority order. It first considers workflow $a$, and
develops a schedule that completes $a$ by its deadline using the minimum
number of node-hours. Once $a$ has been scheduled, SPSS will develop a
low-cost schedule that includes workflow $b$. However, after adding $b$,
the algorithm will determine that the total cost of the combined schedule
for $a$ and $b$ is greater than the budget, and will reject workflow $b$ and
remove it from the schedule. It will then consider workflow $c$, and develop
a low-cost schedule that adds $c$ to the existing schedule for $a$. In order
to complete each job in $c$ by its deadline, SPSS provisions 6 additional
VM-hours. The resulting schedule has a total cost of 16 VM-hours, or
\$16, which is less than the budget of \$18 and completes both $a$ and $c$ by
their deadlines.

>>>>

The deadline of a task $t$ is then:
%
\begin{equation}
\label{eq:spss-deadline}
DL(t) = LST(t) + RT(t) + ST(Level(t))
\end{equation}
%
where $Level(t)$ is the level of $t$, $RT(t)$ is the runtime of $t$, and 
$LST(t)$ is the latest start time of $t$ determined by:
%
$$
LST(t) = \begin{cases}
0,&$if~$Pred(t) = \emptyset\cr
\max_{p \in Pred(t)} DL(p),&$otherwise.$
\end{cases}
$$

@@

To illustrate how the algorithms perform, we prepared an artificial ensemble 
of three workflows, as seen in Fig.~\ref{fig:example-ensemble}. 
The deadline is set to 6 hours and the budget to \$18. In this example we assume
that there are no VM provisioning delays, the runtime estimates are accurate, 
there are no failures and the cost of 1 VM-hour is \$1.
For dynamic algorithms we assume that the low utilization threshold ($u_l$) for deprovisioning is 50\%
and that the autoscaling parameter $v_{max} = 1$.

@@

The final schedule produced by the SPSS algorithm is shown in
Fig.~\ref{fig:algorithms-example-spss}. SPSS generates this schedule by
considering workflows in priority order. It first considers workflow $a$, and
develops a low-cost schedule that completes $a$ by its deadline using a minimum
number of VM-hours. This process involves assigning a deadline to each task
according to Equation~\ref{eq:spss-deadline}, and then scheduling tasks in
deadline-order on the VM that can complete each task by its deadline with the
the minimum increase in cost. Once $a$ has been scheduled, SPSS will develop an
updated low-cost schedule that includes workflow $b$. However, after adding $b$,
the algorithm will determine that the total cost of the combined schedule
for $a$ and $b$ is greater than the budget, and will reject workflow $b$ and
remove it from the schedule. It will then consider workflow $c$, and develop
a low-cost schedule that adds $c$ to the existing schedule for $a$. In order
to complete each job in $c$ by its deadline, SPSS provisions 6 additional
VM-hours, which includes adding an hour to the start time of $VM.2$ for task
$c.60$, adding an hour to the end of $VM.2$ for task $c.45$, adding an hour
to the end of $VM.3$ for $c.50$, adding a new VM, $VM.4$, for 2 hours to run
$c.65$, and finally adding another hour to the end of $VM.2$ for $c.55$. The
resulting schedule has a total cost of 16 VM-hours, or \$16, which is less
than the budget of \$18 and completes both $a$ and $c$ by the deadline.
